\chapter*{Abstract}

Dealing with fire incidents, especially in large recycling centers, poses significant challenges due to their unpredictability and potential for extensive damage. Traditional firefighting methods often fall short, risking human safety and causing environmental pollution. To address this, we propose the use of AI-integrated Fire bots that can make intelligent decisions based on real-time environmental data through various sensors. These Fire bots should be able to: 1) monitor areas for potential fire hazards, 2) detect and promptly extinguish any ongoing fires, and 3) urgently respond to external fire warnings by navigating to the location for inspection or fire suppression.

To ensure the effectiveness of these advanced fire-extinguishing robots, a sophisticated high-level planning is crucial. In this work, we first present existing methodologies and discuss remaining challenges in the field. Afterward, we introduce a novel hybrid task planning module, consisting of a task planner coupled with an Surveillance Algorithm. To the best of our knowledge, this is the first work to combine the two modules, enabling robots to make decisions in complex situations while simultaneously implementing a surveillance system.With the introduction of our hybrid module, we aim to push the boundaries of autonomous fire-extinguishing robotics. We believe they have the potential to significantly enhance the industrial safety by efficiently mitigating the impact of fire accidents in large and complex environments.

The proposed algorithms are tested both in simulations using Gazebo and in real-world scenarios with Turtle Bot3.
